---
title: "Homework 1"
author: "JR Chansakul"
date: 2020-09-14
output: 
  html_document:
    toc: true
---

```{r}
library(tidyverse)
```

# Problem 1

Created a data frame with specified elements. 

```{r Random_sample}
problem1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```


Take the mean of each variable in the data frame:

```{r Mean_sample,collapse = TRUE}
mean (pull(problem1_df, samp))
mean (pull(problem1_df, samp_gt_0))
mean (pull(problem1_df, char_vec))
mean (pull(problem1_df, factor_vec))

```

The mean works for sample and logical vectors, but not character vectors and factor vectors. 

```{r try_numeric, eval=FALSE}
as.numeric (pull(problem1_df, samp))
as.numeric (pull(problem1_df, samp_gt_0))
as.numeric (pull(problem1_df, char_vec))
as.numeric (pull(problem1_df, factor_vec))
```


# Problem 2

```{r Load_penguin}
data("penguins", package = "palmerpenguins")
```

The Penguin dataset contains the following variables:
`r ls(penguins)`

The size of the Penguin dataset contains `r nrow(penguins)` rows or observations and `r ncol(penguins)` columns or 
variables. 

Species is `r class (pull(penguins, species))` variable with 3 categories: `r levels(pull(penguins, species))`.

Island is `r class (pull(penguins, island))` variable with with 3 categories: `r levels(pull(penguins, island))`.







The bill length is a `r class (pull(penguins, bill_length_mm))` variable. The mean bill length is `r mean(pull(penguins, bill_length_mm), na.rm=TRUE)` and the median bill length is `r median(pull(penguins, bill_length_mm), na.rm=TRUE)` . The minimum bill length is `r min((pull(penguins, bill_length_mm)), na.rm = TRUE)`mm and the maximum bill length is `r min((pull(penguins, bill_length_mm)), na.rm = TRUE)`mm.

Bill depth is a `r class (pull(penguins, bill_depth_mm))` variable. The range for bill depth is between `r range (pull(penguins, bill_depth_mm), na.rm = TRUE)`.

Flipper length is a `r class (pull(penguins, flipper_length_mm))` variable. The mean flipper length is
`r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)` and the median flipper length is `r median(pull(penguins, flipper_length_mm), na.rm=TRUE)`.

Body mass index is a `r class (pull(penguins, body_mass_g))` variable. 

Sex is `r class (pull(penguins, body_mass_g))` variable.

Year is `r class(pull(penguins, year))` variable with a range of `r range(pull(penguins, year))`.



Species is `r class (pull(penguins, species))` variable with
`r levels(pull(penguins, species))` levels.

Island is `r class (pull(penguins, island))` variable. 


Year is `r class(pull(penguins, year))` variable



This is the code Scatterplot of flipper_length_mm (y) vs bill_length_mm (x) below. 

```{r Penguin_Scatterplot_FlippervsBill}
ggplot(penguins, aes(bill_length_mm, flipper_length_mm, colour = species)) + geom_point() + ggtitle("Flipper Length (mm) vs Bill Length (mm)") + theme(plot.title = element_text(hjust = 0.5))
ggsave("scatter_plot.pdf", height = 4, width = 6)
```





